Fig2: Candidate genes

### 2020-05-06 analysis/figure-2.Rmd
new fig 2

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~sex, scales = "free_y", nrow = 1) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          axis.title.y = element_text(face = "italic"),
          axis.text.x = element_blank(),
          axis.ticks = element_blank()) +
    labs(y = whichgenes,
         x = NULL) +
    geom_signif(comparisons = list(c( "control", "bldg"),
                                 c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0)

@@

header <- png::readPNG("../figures/images/fig_fig2a.png")
header <- ggdraw() +  draw_image(header, scale = 1)

b <- plotcorrplot(hyp3, "females and males") + theme(legend.position = "none")  + labs(title = "Hypothalamus")
g <- plotcorrplot(pit3, NULL) + theme(legend.position = "none") + labs(title = "Pituitary")
l <- plotcorrplot(gon3, NULL) + theme(legend.position = "none")  + labs(title = "Gonad")

c <- scattercorrelations(FH, FH$DRD1, FH$HTR2C, "#969696", "DRD1", "HTR2C") + labs(subtitle = "female") + labs(title = "")
h <- scattercorrelations(FP, FP$AVPR1A, FP$CRHR1, "#969696", "AVPR1A", "CRHR1")  + labs(subtitle = NULL)+ labs(title = "")
m <- scattercorrelations(FG, FG$ESR1, FG$PGR, "#969696", "ESR1", "PGR")   + labs(subtitle = NULL)+ labs(title = "")

d <- scattercorrelations(MH, MH$DRD1, MH$HTR2C, "#525252", "DRD1", "HTR2C")  + labs(subtitle = "male") + labs(title = "")
i <- scattercorrelations(MP, MP$AVPR1A, MP$CRHR1, "#525252", "AVPR1A", "CRHR1")  + labs(subtitle = NULL) + labs(title = "")
n <- scattercorrelations(MG, MG$ESR1, MG$PGR, "#525252", "ESR1", "PGR")  + labs(subtitle = NULL) + labs(title = "")

d1 <- candidateboxplot("hypothalamus", c("DRD1"), sexlevels) + labs(x = NULL , title = " ")  + theme(axis.line.x = element_blank()) 
d2 <- candidateboxplot("hypothalamus", c("HTR2C"), sexlevels) + labs(x = "Parental stage" ) + theme(strip.text = element_blank())

g1 <- candidateboxplot("pituitary", c("AVPR1A"), sexlevels) + labs(x = NULL, title = " " )  + theme( strip.text = element_blank(), axis.line.x = element_blank())
g2 <- candidateboxplot("pituitary", c("CRHR1"), sexlevels) + labs(x = "Parental stage"  )  + theme(strip.text = element_blank())

j1 <- candidateboxplot("gonad", c("ESR1"), sexlevels) + labs(x = NULL , title = " ") + theme(strip.text = element_blank(), axis.line.x = element_blank())
j2 <- candidateboxplot("gonad", c("PGR"), sexlevels) + labs(x = "Parental stage"  ) + theme(strip.text = element_blank())

btn <- plot_grid(b,c,d, g,h,i,l,m,n, ncol = 3, labels = c("B", "C", " ","E", "F", " ", "H", "I"), label_size = 8, rel_widths = c(1.4,1,1), rel_heights = c(1.1,1,1))
dgj <- plot_grid(d1,d2,g1,g2,j1,j2, ncol = 1, labels = c("D", " ", "G", " " , "J"), label_size = 8, rel_heights = c(1.3,1,1.2,1,1.2,1))
btoj <- plot_grid(btn,dgj, ncol = 2 , rel_widths = c(1.75,1))

plot_grid(header, btoj,  rel_heights = c(0.2,1), ncol = 1)

>>>>

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~sex,  nrow = 1) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          axis.title.y = element_text(face = "italic"),
          axis.text.x = element_blank(),
          axis.ticks = element_blank()) +
    labs(y = whichgenes,
         x = NULL) +
    geom_signif(comparisons = list(c( "control", "bldg"),
                                 c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0)

@@

a <- png::readPNG("../figures/images/fig_fig2a.png")
a <- ggdraw() +  draw_image(a, scale = 1)

b1 <- plotcorrplot(hyp3, "females and males") + theme(legend.position = "none")  + labs(y = "Hypothalamus", title = "Candidate gene correlations")
b2 <- plotcorrplot(pit3, NULL) + theme(legend.position = "none") + labs(y = "Pituitary")
b3 <- plotcorrplot(gon3, NULL) + theme(legend.position = "none")  + labs(y = "Gonad")

c1 <- scattercorrelations(FH, FH$DRD1, FH$HTR2C, "#969696", "DRD1", "HTR2C") + labs(subtitle = "female", title =  "Top correlation")  
c3 <- scattercorrelations(FP, FP$AVPR1A, FP$CRHR1, "#969696", "AVPR1A", "CRHR1")  + labs(subtitle = NULL) 
c5 <- scattercorrelations(FG, FG$ESR1, FG$PGR, "#969696", "ESR1", "PGR")   + labs(subtitle = NULL)

c2 <- scattercorrelations(MH, MH$DRD1, MH$HTR2C, "#525252", "DRD1", "HTR2C")  + labs(subtitle = "male", title = "", y = NULL)  
c4 <- scattercorrelations(MP, MP$AVPR1A, MP$CRHR1, "#525252", "AVPR1A", "CRHR1")  + labs(subtitle = NULL, y = NULL)  
c6 <- scattercorrelations(MG, MG$ESR1, MG$PGR, "#525252", "ESR1", "PGR")  + labs(subtitle = NULL, y = NULL)

d1 <- candidateboxplot("hypothalamus", c("DRD1"), sexlevels) + labs(x = NULL, title = "Temporal expression pattern" )  
d2 <- candidateboxplot("hypothalamus", c("HTR2C"), sexlevels) + labs(x = NULL ) + theme(strip.text = element_blank())
d3 <- candidateboxplot("pituitary", c("AVPR1A"), sexlevels) + labs(x = NULL )  + theme( strip.text = element_blank())
d4 <- candidateboxplot("pituitary", c("CRHR1"), sexlevels) + labs(x = NULL  )  + theme(strip.text = element_blank())
d5 <- candidateboxplot("gonad", c("ESR1"), sexlevels) + labs(x = NULL) + theme(strip.text = element_blank())
d6 <- candidateboxplot("gonad", c("PGR"), sexlevels) + labs(x = NULL ) + theme(strip.text = element_blank())

b <- plot_grid(b1,b2,b3, ncol = 1, rel_heights = c(1.1,1,1))
c <- plot_grid(c1,c2,c3,c4,c5,c6, ncol = 2, rel_heights = c(1.1,1,1), rel_widths = c(1.1,1))
d <- plot_grid(d1,d2,d3,d4,d5,d6, ncol = 1, rel_heights = c(1.1,1.1, 1,1, 1,1))

bcd <- plot_grid(b,c,d, ncol = 3, rel_widths = c(1,1,1), labels = c("B", "C", "D"), label_size = 8)

fig2 <- plot_grid(a,bcd, ncol = 1, labels = c("A"), label_size = 8, rel_heights = c(0.1,1))
fig2
```
